### 2020-09-25 text/article_vedrovice.Rmd
correct figures

<!-- The size of the radius is based on the results of nearest neighbors analysis, where
at the given radius there is strong evidence of a clustering process (Fig. \@ref(fig:spat-funs)).
The randomness is again tested using a permutation test similar to the one
described for the neighborhood derived from the graphs.-->

@@

<!-- The quadrat test shows evidence for both random and clustered processes taking place with p values
under the 0.05 alpha level but the $\chi^2$ approximation is inaccurate due to small
expected counts (for the details see supplementary information).
Inconclusive result of the quadrat test is not suprising because as was noted
earlier, we do not expect *first-order* properties to play major roles in
placing of the individual burials. -->
Results of functions based on nearest neighbors are reported in Fig. \@ref(fig:spat-funs).
Both *G* and  *F* functions do slightly deviate from the curve expected
under independent random process
but neither traverses the boundaries of the envelope.
Thus the cummulative nearest-neighbor distance (*G*) as well as the
empty-space function *F* are well approximated by
random process and do not show evidence for spatial clustering nor repelent functions
taking place.
On the contrary
the *K* and *T* functions show clear deviations from the expected curve and both exceed
the boundaries of given envelopes at distances around or smaller than 5 meters.
<!-- in case of *K* and slightly more in case of *T* function.-->
This means that numbers of nearest neighbors at this and larger distances is
significantly higher than we would expect under complete spatial randomness.
The overall point pattern thus shows clear signs of clustering process taking place.

@@

```{r sstat, fig.cap = "Distribution of simulated and observed *S* statistic"}
knitr::include_graphics(here("plots/s_statistic.pdf"))
```

```{r vstat, fig.cap = "Simulated and observed *V* statistics for different variables"}
knitr::include_graphics(here("plots", "v_values.pdf"))
```

```{r coocnets, fig.cap = "Networks of variables frequently present together and exluding each other"}
knitr::include_graphics(here("plots", "cooc_networks.pdf"))
```

<!-- ```{r plan-graphs, fig.cap = "Neighborhood graphs: Delaunay triangulation and Gabriel graph"} -->
<!-- knitr::include_graphics(here("plots/plan_gabriel.pdf")) -->
<!-- ``` -->

<!-- ```{r label-spat-funs} -->
<!-- label_spat_funs <- paste("Functions *G*, *F*, *K* and *T*.", -->
<!-- "*Dashed line* -- theoretical curve under complete spatial randomness, *solid line* -- empirical curve, *gray area* -- envelope.") -->
<!-- ``` -->
<!-- ```{r spat-funs, fig.cap=label_spat_funs} -->
<!-- knitr::include_graphics(here("plots/pointprocess_fun.pdf")) -->
<!-- ``` -->

<!-- ```{r label-nb-sex} -->
<!-- label_nb_sex <- paste("Mean neighbors in a given sex category.", -->
<!-- "*Gray area* -- density estimation for the simulated data, *vertical line* -- observed value.", -->
<!-- "*F* -- female-sexed body, *M* -- male-sexed body, *n. a.* -- non adult, *ind.* -- indetermined sex.") -->
<!-- ``` -->
<!-- ```{r nb-sex, fig.cap=label_nb_sex} -->
<!-- knitr::include_graphics(here("plots/nb_sex.pdf")) -->
<!-- ``` -->

>>>>

<!-- The size of the radius is based on the results of nearest neighbors analysis, where
at the given radius there is strong evidence of a clustering process (Fig. \@ref(fig:pp-funs)).
The randomness is again tested using a permutation test similar to the one
described for the neighborhood derived from the graphs.-->

@@

<!-- The quadrat test shows evidence for both random and clustered processes taking place with p values
under the 0.05 alpha level but the $\chi^2$ approximation is inaccurate due to small
expected counts (for the details see supplementary information).
Inconclusive result of the quadrat test is not suprising because as was noted
earlier, we do not expect *first-order* properties to play major roles in
placing of the individual burials. -->
Results of functions based on nearest neighbors are reported in Fig. \@ref(fig:pp-funs).
Both *G* and  *F* functions do slightly deviate from the curve expected
under independent random process
but neither traverses the boundaries of the envelope.
Thus the cummulative nearest-neighbor distance (*G*) as well as the
empty-space function *F* are well approximated by
random process and do not show evidence for spatial clustering nor repelent functions
taking place.
On the contrary
the *K* and *T* functions show clear deviations from the expected curve and both exceed
the boundaries of given envelopes at distances around or smaller than 5 meters.
<!-- in case of *K* and slightly more in case of *T* function.-->
This means that numbers of nearest neighbors at this and larger distances is
significantly higher than we would expect under complete spatial randomness.
The overall point pattern thus shows clear signs of clustering process taking place.

@@

<!-- randomization -->
<!--
```{r sstat, fig.cap = "Distribution of simulated and observed *S* statistic"}
# knitr::include_graphics(here("plots/s_statistic.pdf"))
```

```{r vstat, fig.cap = "Simulated and observed *V* statistics for different variables"}
# knitr::include_graphics(here("plots", "v_values.pdf"))
```

```{r coocnets, fig.cap = "Networks of variables frequently present together and exluding each other"}
# knitr::include_graphics(here("plots", "cooc_networks.pdf"))
```
-->

<!-- plans -->

<!-- point pattern analysis -->

```{r label-pp-funs}
label_pp_funs <- paste("Functions *G*, *F*, *K* and *T*.",
"*Dashed line* -- theoretical curve under complete spatial randomness, *solid line* -- empirical curve, *gray area* -- envelope")
```
```{r pp-funs, fig.cap=label_pp_funs}
knitr::include_graphics(here("text/figs/pp_funs.pdf"))
```

```{r label-pp-crossk}
label_crossk <- paste("Multitype K function for different categorical variables, for legend see previous Fig.")
```
```{r pp-crossk, fig.cap=label_crossk}
knitr::include_graphics(here("text/figs/pp_crossk.pdf"))
```

<!-- neighborhood -->
```{r plan-graphs, fig.cap="Neighborhood graphs: Delaunay triangulation and Gabriel graph"}
knitr::include_graphics(here("text/figs/plan_graphs.pdf"))
```

<!-- to SI
```{r label-nb-sex}
label_nb_sex <- paste("Mean neighbors in a given sex category.",
"*Gray area* -- density estimation for the simulated data, *vertical line* -- observed value;",
"*F* -- female-sexed body, *M* -- male-sexed body, *n. a.* -- non-adult body")
```
```{r nb-sex, fig.cap=label_nb_sex}
knitr::include_graphics(here("text/figs/nb_sex.pdf"))
```

```{r label-nb-age}
label_nb_age <- paste("Mean neighbors in a given age category.",
"*Gray area* -- density estimation for the simulated data, *vertical line* -- observed value;",
"*F* -- female-sexed body, *M* -- male-sexed body, *n. a.* -- non-adult body")
```
```{r nb-age, fig.cap=label_nb_age}
knitr::include_graphics(here("text/figs/nb_age.pdf"))
```
-->

<!-- percolation analysis -->

```{r perc-distance, fig.cap="Percolation thresholds"}
knitr::include_graphics(here("text/figs/perc_distance.pdf"))
```

```{r perc-plan, fig.cap="Clusters formed at given percolation threshold distances"}
knitr::include_graphics(here("text/figs/perc_plan_ids.pdf"))
```
